Wikipedia Text Mining and Entropy Analysis

### 2018-09-18 wiki_entropy.Rmd
More wikipedia data (Italian, Norwegian, Dutch, Romanian)

```{python}
import regex as re 
import numpy as np
import pandas as pd

@@

text = extract_texts(20)
ar_df = get_sen_df(text)
```

@@

entropies <- map(6:12, ~get_entropies(.x, py$ar_df)) %>%
  bind_rows()

>>>>

```{python, include=FALSE}
import regex as re 
import numpy as np
import pandas as pd

@@

text = extract_texts(50)
ro_df = get_sen_df(text)
```

@@

entropies <- map(6:12, ~get_entropies(.x, py$ro_df)) %>%
  bind_rows()
